### 2024-07-01 causal-inference.qmd
20240701 - loops and reorganization

A key tool when describing a research question or hypothesis is to create a conceptual depiction of the hypothesized causal processes.
A causal diagram depicts the hypothesized causal processes that link two or more variables.
A common form of causal diagrams is the directed acyclic graph (DAG).
DAGs provide a helpful tool to communicate about causal questions and help identify how to avoid bias (i.e., over-estimation) in associations between variables due to confounding (i.e., common causes) [@Digitale2022].
You can use the `R` package `dagitty` [@Textor2017] or the associated browser-based extension, DAGitty: https://dagitty.net (archived at https://perma.cc/U9BY-VZE2) to create DAGs.
Examples of various causal diagrams that could explain why `X` is associated with `Y` are in @fig-XCausesY, @fig-YCausesX, and @fig-ZCausesXandY.

>>>>

A key tool when describing a research question or hypothesis is to create a conceptual depiction of the hypothesized causal processes.
A causal diagram depicts the hypothesized causal processes that link two or more variables.
A common form of causal diagrams is the directed acyclic graph (DAG).
DAGs provide a helpful tool to communicate about causal questions and help identify how to avoid bias (i.e., over-estimation) in associations between variables due to confounding (i.e., common causes) [@Digitale2022].
For instance, from a DAG, it is possible to determine what variables it is important to control for in order to get unbiased estimates of the association between two variables of interest.
To create DAGs, you can use the `R` package `dagitty` [@Textor2017] or the associated browser-based extension, DAGitty: https://dagitty.net (archived at https://perma.cc/U9BY-VZE2).
Examples of various causal diagrams that could explain why `X` is associated with `Y` are in @fig-XCausesY, @fig-YCausesX, and @fig-ZCausesXandY.

### 2024-07-01 getting-started.qmd
20240701 - loops and reorganization

>>>>

## Loops {#sec-loops}

If you want to perform the same computation multiple times, it can be faster to do it in a loop compared to writing out the same computation many times.
For instance, here is a loop that prints each element of a vector and the loop index (`i`) that indicates where the loop is in terms of its iterations:

for(i in 1:length(players$ID)){
  print(paste("The loop is at index:", i, sep = " "))
  print(paste("My favorite player is:", players$name[i], sep = " "))
}
```
